An Example

### 2019-09-03 R/rmarkdown.Rmd
add border to pdf to distingish it from backround closes #39

---
title: "An Example"
author: "Aaron Peikert & Andreas Brandmaier"
date: "9/3/2019"
output: pdf_document
papersize: "a6"
geometry:
  - "landscape"
  - margin=0.1cm
---

>>>>

---
title: "An Example"
author: "Aaron Peikert & Andreas Brandmaier"
date: "9/3/2019"
output: pdf_document
papersize: "a6"
geometry:
  - "landscape"
  - margin=0.5cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---
